---
title: "ISLR Chapter 4 Lab"
output: html_document
---

### Libraries
```{r}
library('tidyverse')
library('ISLR')
```

<br>

The dataset we'll use first:

```{r}
head(Smarket)
```

<br>

```{r}
pairs(Smarket)
```

<br>

```{r}
cor(Smarket[,-9])
```

<br>

We can see that volume is increasing over time. 

```{r}
plot(Smarket$Volume)
```

<br>

## Logistic Regression

Predicting Direction using Lag1, ..., Lag5 and Volume. 

```{r}
head(Smarket)
```


```{r}
logistic_1 <- glm(Direction ~ . - Today - Year, data = Smarket, family = binomial)
summary(logistic_1)
```

<br>

Coefficient function -

```{r}
coef(logistic_1)
```

<br>

This does the same thing - 

```{r}
summary(logistic_1)$coefficient[,1]
```

<br>

Predict function for logistic -

```{r}
logit_1_prob <- predict(logistic_1, type = 'response')
logit_1_prob[1:10]
```

<br>

But which way is 1? up or down?

```{r}
contrasts(Smarket$Direction)
```

<br>

In order to turn a prediction into up or down, we'll create those classes corresponding to the probabilities.

```{r}
logit_1_pred <- rep('Down', 1250)
logit_1_pred[logit_1_prob > 0.5] = 'Up'
head(logit_1_pred)
```

<br> 

### Training and Test Set

```{r}
train <- (Smarket$Year < 2005)
Smarket_2005 <- Smarket[!train,]
dim(Smarket_2005)
dir_2005 <- Smarket$Direction[!train]
```

<br>

```{r}
glm_fits <- glm(Direction ~ . - Today - Year, data = Smarket, family = 'binomial', subset = train)

glm_prob <- predict(glm_fits, Smarket_2005, type = 'response')
```

<br>

let's see the results

```{r}
glm_pred <- rep('Down', 252)
glm_pred[glm_prob > 0.5] <- 'Up'

table(glm_pred, dir_2005)
mean(glm_pred == dir_2005)
```

<br>

The above we guess correctly less than 50% of the time, terrible. 

Let's refit the model using only the best predictors. 

```{r}
glm_fits$coefficients
```

<br>

```{r}
glm_fits <- glm(Direction ~ Lag1 + Lag2, data = Smarket, subset = train, family = 'binomial')
```

<br>

```{r}
glm_probs <- predict(glm_fits, Smarket_2005, type = 'response')

glm_pred <- rep('Down', 252)
glm_pred[glm_probs > 0.5] <- 'Up'

table(glm_pred, dir_2005)
mean(glm_pred == dir_2005)
```

<br> 

56% of the time we correctly predicted which way the stock market is moving, by taking away variables!

<br> 

Predicting based on a specific value of Lag1 and Lag2

```{r}
predict(glm_fits, 
        newdata = data.frame(Lag1 = c(1.2, 1.5), Lag2 = c(1.1, -0.8)),
        type = 'response')
```

The prediction is a down market for each o those lags. 


