---
title: "K-Nearest Neighbors"
author: "Fisher Ankney"
output: html_document
---

```{r}
library('tidyverse')
library('ISLR')
library('class')
```

```{r}
?knn
```

Requires 4 inputs - 

- train: a matrix containing the predictors associated with training data
- test: a matrix containing the predictors we want to make prediction upon
- cl: a vector containing the class labels for training observations (train.Direction)
- K: the number of nearest neighbors to be used

<br>

According to the above requirements, we want Lag1 and Lag2 of the Smarket dataset to share a matrix for training and a matrix for testing. 

first we'll make the training data - 

```{r}
train <- (Smarket$Year < 2005)
Smarket_2005 <- Smarket[!train,]
dir_2005 <- Smarket$Direction[!train]
```


<br> 

Now we can make the matrix inputs and an associated training direction object - 

```{r}
train_x <- cbind(Smarket$Lag1, Smarket$Lag2)[train, ]
test_x <- cbind(Smarket$Lag1, Smarket$Lag2)[!train, ]

train_dir <- Smarket$Direction[train]
```

<br> 

Knn uses an element of randomness to break ties in lengths, set a seed before conducting

```{r}
set.seed(2)

knn_pred <- knn(train_x, test_x, train_dir, k = 1)
table(knn_pred, dir_2005)
mean(knn_pred == dir_2005)

```

<br> 

automate finding the best k - 

```{r}
outputs <- vector('double', length = 50)


for (i in 1:50) {
  knn_pred <- knn(train_x, test_x, train_dir, k = i)
  outputs[i] <- mean(knn_pred == dir_2005)
  i <- i + 1
}

which.max(outputs)
```

<br> 

```{r}
knn_pred <- knn(train_x, test_x, train_dir, k = 3)
mean(knn_pred == dir_2005)
```

53% accuracy with the best K. 

