---
title: 'Categorical Variable Regression'
output: html_document
---


When one or more of your preditors is categorical, instead of continuous, make use of dummy variable. 

<br> 

## Single Predictor

simple case, you have to predict height based on gender. 

```{r}
gender <- c(rep('m', 50), rep('f', 50))
height <- c(rnorm(50, mean = 125, sd = 10), rnorm(50, mean = 100, sd = 10))
```

<br>

turn your predictor categorical

```{r}
gender <- as.factor(gender)
```

<br> 

```{r}

boxplot(height ~ gender)

model <- lm(height ~ gender)

```

<br> 

```{r}
model <- lm(height ~ gender)
summary(model)
```

$\beta_1$ coefficient, genderm, is the difference between gender male and gender female. this case it is 23, the model was actually 25. 


intercept is the average height of the reference category, gender female. 

intercept + beta_1 is the average height of the secondary category, x = 1, male. 

our dummy variable is x = 0 female, x = 1 male, as seen here

```{r}
contrasts(gender)
```

<br> 

## Multiple Predictors

one of the predictors is categorical

very similiar interpretation

<br> 

## Multipe Categories 

need t-1 dummy variables, can't have x = 0, x = 1, x = 2. that emplies an interval relationship. we want categorical. 





