---
title: 'Confidence Intervals'
output: html_document
---

## Set Up

```{r, message = F}
library('tidyverse')
set.seed(9)

# generate data
x <- sample(1:100, replace = T)
eps <- rnorm(100, 0, 35)
y <- 3 * x + 1 + eps 

# create slr
fit <- lm(y ~ x)

# plot
plot(y ~ x, col = 'firebrick') # points
lines(abline(1,3, col = 'firebrick', lwd = 2)) # actual
lines(abline(fit, col = 'slateblue', lwd = 2)) # model
```

<br> 

## Confidence Interval of Coefficients

```{r}
confint(fit)
```

2.5% and 97.5% are percentiles, meaning 95% is between these two values. Intercept is $\beta_0$, x coefficient is $\beta_1$. in this case, $\beta_1$ is not inside the confidence interval. 

<br> 

## Testing the 95% CI

it's the interval that has a random component, not beta_1. to prove this, lets generate 100 models of the data. Beta 1 remains to be 3 for each model. the samples change, thus the beta_1 hat estimator changes, and corresponding confidence interval changes. 

<br> 

```{r}
beta_low <- vector('double', length = 100)
beta_high <- vector('double', length = 100)

for(i in 1:100) {
  
  set.seed(i+100)
  
  x <- sample(1:100, replace = T)
  eps <- rnorm(100, 0, 35)
  y <- 3 * x + 1 + eps 
  
  fit <- lm(y ~ x)
  
  beta_low[i] <- confint(fit)[2,1]
  beta_high[i] <- confint(fit)[2,2]
  
  i <- i + 1
}

dat <- data.frame(low = beta_low, high = beta_high, index = 1:100)

ggplot(dat) + 
    geom_segment(aes(y = 3, yend = 3, x = 0, xend = 100)) + 
    geom_segment(aes(x = 1:100, y=low[1:100], yend = high[1:100], xend = 1:100)) +
    theme_minimal()
```

<br> 


## Confidence Band

A confidence band tells us that the average value for a prediction will be within the lower and upper limits 95% of the time. That is' the model itself will be between those two values. 

<br> 

```{r}
# create the bands
sample <- data.frame(y = y, x = x, interval = 1:100)

fit <- lm(y ~ x, data = sample)

sample$CI <- predict(fit, interval = 'confidence', newdata = data.frame(interval = 1:100))

ggplot(sample) + 
  geom_point(aes(y=y, x=x)) + 
  geom_line(aes(x = 1:100, y = sample$CI[,2]))


sample$CI[,2]
```


```{r}
sample$CI
ggplot(sample, aes(y = y, x = x)) + 
  geom_point() + 
  stat_smooth(method = 'lm', level = 0.95)

?stat_smooth



dat$low_ci 
dat$low_ci <- predict(fit, newdata = , 
                        interval = "confidence", 
                        level = 0.9)[, 2]
nd1_eng$HiCI <- predict(mod1, newdata = nd1_eng, 
                        interval = "confidence", 
                        level = 0.9)[, 3]

source <- data.frame(y = y, x = x)
predict(fit)

ggplot() + 
  geom_point(aes(y = y, x = x)) + 
  geom_line(aes(y = dat$high, x = dat$index)) + 
  theme_minimal()
```


```{r, eval = F}
predict(interval = 'confidence')
```






## prediction band

Says that the data points will be between the lower and upper limit. 


```{r, eval = F}
predict(interval = 'prediction')
```

<br> 

## Simultaneous correction

Bonferroni 


