---
title: 'Linear Dependence'
output: html_document
---

## Covariance 

$\sigma_{xy}$ is covariance

$\sigma_{xy} = E(XY) - E(X)E(Y)$

Covariance is the measure indicating the extent that two variables change in tandem. not bounded by any numbers, can be positive or negative. 

Linear relationship.

changes in scale effect covariance


```{r, eval = F}
cov(x,y)
```

<br> 

## Correlation


Correlation is $r$

scaled measurement of how strong a two variables linear relationship is. 

$-1 < r < 1$

where perfect linear negative correlation = -1 and perfect linear positive correlation = 1, absolutely linearly uncorrelated = 0. 

$r = \frac{\sigma_{xy}}{\sigma_x \sigma_y}$

<br> 

Dependent on covariance, but scaled by individual variances. 

To test correlation use: 

```{r, eval = F}
cor.test(x,y)
```

<br> 

## Importance of Visualization

insert anscombs quartet

<br> 

## Interpretation

perfect postive linear relationship

good positive linear relationship

poor positive linear relationship

good linear relationship

correlation of zero doesn't mean uncorrleated, just linearly uncorrelated

independent does mean correlation of zero

<br> 

## Related Concepts

basis of R squared (link)




