---
title: 'Simple Linear Regression'
output: html_document
---

## Mathematical Model 

Once you've decided that theres a linear correlation between two data points (link), a simple linear regression model could work. 

<br> 

Prediction of one variable from knowledege of another. 

Assuming a simple linear relationship between two variables, there exists a relationship of this form: 

$$ y = \beta_0 + \beta_1 x_1 + \epsilon $$

Where: 

$y$: the predicted variable 

$\beta_0$: the y-intercept 

$\beta_1$: the slope of x_1 

$x_1$: the predicting variable

$\epsilon$: the error term  


<br> 

we estimate this relationship with the model:

Mathematical Model: 

$$ \hat{y} = \hat{\beta_0} + \hat{\beta_1} x_1 $$

Where

$\hat{y}$ the estimated value of the dependent, predicted variable

$\hat{\beta_0}$ the estimate value of the y-intercept

$\hat{\beta_1}$ the estimate value of the slope, or x coefficient

$x_1$ the independent, or predictor variable 


<br> 

Relies on assumptions, found in this post (link). 

<br> 


## Simulating Data

```{r}
library(tidyverse)
set.seed(10)

# create data
x <- rnorm(100, mean = 60, sd = 20)
eps <- rnorm(100, mean = 0, sd = 25)
y <- 2*x + 1 + eps

# plot data with true model
ggplot() + 
  geom_point(aes(y = y, x = x), color = 'darkblue') + 
  theme_minimal() +
  ggtitle('Generated Data')
```

<br> 

## True Relationship

```{r}
# fitting the true line
ggplot() + 
  geom_point(aes(y = y, x = x), color = 'darkblue') + 
  geom_line(aes(y = 2*x + 1, x = x), 
            size = 1.25, color = 'darkblue') + 
  theme_minimal() +
  ggtitle('True Regression Line')
```


<br> 

## Simple Linear Regression Model 

```{r}
sim_dat <- tibble(x = x, y = y)

fit <- lm(y ~ x, data = sim_dat)

sim_dat %>% 
  mutate( model = predict(fit) ) %>%
  ggplot() + 
  geom_point(aes(y = y, x = x), color = 'darkblue') + 
  geom_line(aes(y = 2*x +1, x = x), 
            size = 1.25, color = 'darkblue') + 
  geom_line(aes(y = model, x = x), 
            size = 1.25, color = 'firebrick') + 
  theme_minimal() +
  ggtitle('True Line & Regression Model')
```

<br> 

## Interpretation

<br> 

```{r}
summary(fit)
```

<br> 


The real relationship was y = 2x + 1 

meaning: 

$\beta_0 = 1$

$\beta_1 = 2$

and we set the error term with 

```{r, eval = F}
eps = rnorm(100, mean = 0, sd = 25)
```

Meaning we wanted random normal error, that centered at the x value, with a standard deviation of 25. 

<br> 

Our model supposes the relationship is y = 1.92 x + 2.9

Meaning:

$\hat{\beta_0}$: 2.9

$\hat{\beta_1}$: 1.92

<br> 


It did a good job in following the true regression line as seen in the comparison plot. 

<br> 

## Related Concepts

To learn more about specific interpretation, follow the link you wish: 

- Residual Squared Error (RSE) 
- R Squared
- Hypothesis Testing Linear Models



