---
title: "Discriminant Analysis"
author: "Fisher Ankney"
output: html_document
---

```{r, message = F}
library('tidyverse')
library('ISLR')
library('MASS')
```

<br>

### Linear Discriminant Analysis

fit an lda model using the lda function! same syntax excep the absence of a family option. 
```{r}
?lda
```

<br>

setting up the data into train and test

```{r}
train <- (Smarket$Year < 2005)
Smarket_2005 <- Smarket[!train,]
dir_2005 <- Smarket$Direction[!train]
```

<br>

fitting an lda model - 

```{r}
lda_fit <- lda(Direction ~ Lag1 + Lag2, data = Smarket, subset = train)
lda_fit
```

<br>

this is the computation of the coefficients times each of the training observations - 

```{r}
plot(lda_fit)
```

<br> 

Making the prediction - 

```{r}
lda_pred <- predict(lda_fit, Smarket_2005)
```

<br> 

Calculating prediction accuracy - 

```{r}
lda_class <- lda_pred$class
table(lda_class, dir_2005)
mean(lda_class == dir_2005)
```

<br>

That's 56% accuracy in the prediction, which is nearly spot on with the logistic regression prediction accuracy. 


<br> 

### Quadratic Discriminant Analysis 

<br> 

```{r}
?qda
```

<br>

No wonder these predictions are terrible, we're trying to group this: 

```{r}
ggplot(Smarket) + 
  geom_point(aes(x = Lag1, y = Lag2, color = Direction))
```

<br> 

Create the model - 

```{r}
qda_fit <- qda(Direction ~ Lag1 + Lag2, data = Smarket, subset = train)
qda_fit
```

<br> 

Create the prediction - 

```{r}
qda_pred <- predict(qda_fit, Smarket_2005)
class <- qda_pred$class
```

<br>

Check validity - 

```{r}
table(class, dir_2005)
mean(class == dir_2005)
```

<br>

wow, 60% accuracy.


